Uranyl solvation by a three-dimensional reference interaction site model

### 2015-04-17 doc/uo2_paper/uo2-II.tex
AM: textcolor is not used anymore

%% LyX 2.0.6 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[english,journal=jpcafh,manuscript=article,layout=twocolumn,maxauthors=0]{achemso}
\usepackage[T1]{fontenc}
\usepackage{color}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{esint}
\usepackage[numbers]{natbib}

@@

The solvation energy of uranyl is estimated as\textcolor{green}{{} }
\begin{equation}
\Delta G_{\text{sol}}=G[\text{UO}_{2}(\text{H}_{2}\text{O})_{n}^{2+}]-nG[\text{H}_{2}\text{O}]-E[\text{UO}_{2}^{2+}]\label{eq:dG-sol-definition}
\end{equation}
for $n\ge0$ explicit aqua ligands. Note that without proper statistical
sampling over the solute degrees of freedom $s$ this approximation
of the solvation energy, justified to some extent for sufficiently
rigid solutes, does not hold for systems with a large number $n\to\infty$
of explicit water molecules outside of the tightly bound first solvation
shell. Indeed, in a gedanken experiment the difference $G[(\text{H}_{2}\text{O})_{n}]-nG[\text{H}_{2}\text{O}]$
for the above definition of $G$ applied to water droplets asymptotically
approaches $n(\bar{E}[\text{H}_{2}\text{O}]-G[\text{H}_{2}\text{O}])$
where $\bar{E}$ is the average configurational energy of a water
molecule; its value is about $-$9.9~kcal/mol \citep{Berendsen87,Mahoney00}.
This result is to be compared to the solvation energy of $-$6.3~kcal/mol
derived from the ratio of the equilibrium vapor/liquid concentrations
\citep{Bridgeman64}.

@@

Indeed, the behavior of another convolution operand at low $k$, the
solvent susceptibility is regular 
\begin{equation}
\tilde{\chi}_{\alpha\gamma}(k)\sim\rho\kappa+\frac{1}{2}d_{\alpha\gamma}k^{2}
\end{equation}
with the limit for $k\to0$ being proportional to the solvent compressibility
$\kappa$ (here in temperature units) \citep{book:Hansen06}. More
importantly, this limit is the same for all site pairs $\alpha$ and
$\gamma$. Though not enforced, this property is obeyed with reasonable
accuracy in practical calculations. The second term, of $o(k^{2})$,
is site pair specific and is in particular responsible for the dielectric
response of the solvent. This term is addressed by the dielectric
correction in the DRISM approach \citep{Perkyns92,Cummings81,Kovalenko00b}.
The result of the\textcolor{blue}{{} }convolution, 
\begin{equation}
\tilde{\tau}_{\alpha}(\vec{k})=\tilde{n}(\vec{k})\tilde{\theta}_{\alpha}(k)\label{eq:tau}
\end{equation}
expressed here via the regular auxiliary functions
\begin{equation}
\tilde{\theta}_{\alpha}(k)=\tilde{\varphi}(k)\sum_{\gamma}\tilde{\chi}_{\alpha\gamma}(k)q_{\gamma}\sim2\pi\sum_{\gamma}d_{\alpha\gamma}q_{\gamma}\label{eq:theta}
\end{equation}
is also regular for an overall neutral solvent, $\sum_{\gamma}q_{\gamma}=0$.
In that case, the compressibility term in Eq.~\ref{eq:theta} vanishes
after summation. Note that the functions $\tilde{\theta}_{\alpha}(k)$
(one per solvent site $\alpha$) are convolutions of spherically symmetric
functions neither of which is solute specific. The functions $\tilde{\theta}_{\alpha}(k)$
are site-specific solvent properties which represent the response
to a unit charge (here broadened as a Gaussian). These quantities
can be computed using 1D techniques, just as the solvent susceptibility
$\tilde{\chi}_{\alpha\gamma}(k)$ itself. In the 1D case our deliberate
choice of the self-inverse discrete sine transform of type IV (DST-IV)
as a basic operation eliminates the need for treating the singularities
at $r=0$ and $k=0$ as the discrete representation does not include
these points by construction \citep{FFTW05}. A similar approach was
applied before to a monopole field of the solute \citep{Kloss08b}
and to a superposition of Gaussian-type charge distributions \citep{Perkyns10}.

@@

\begin{figure}[tbph]
\caption{Potential of mean\textcolor{blue}{{} }force, $W(\varrho,z)$, for the
U--O$_{\text{w}}$ distribution function, determined with the closure
PSE1. $\varrho$ and $z$ are the radial and axial displacements from
the uranium center. \label{fig:potential-of-mean-force-2d}}

>>>>

%% LyX 2.0.6 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[english,journal=jpcafh,manuscript=article,layout=twocolumn,maxauthors=0]{achemso}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{esint}
\usepackage[numbers]{natbib}

@@

The solvation energy of uranyl is estimated as
\begin{equation}
\Delta G_{\text{sol}}=G[\text{UO}_{2}(\text{H}_{2}\text{O})_{n}^{2+}]-nG[\text{H}_{2}\text{O}]-E[\text{UO}_{2}^{2+}]\label{eq:dG-sol-definition}
\end{equation}
for $n\ge0$ explicit aqua ligands. Note that without proper statistical
sampling over the solute degrees of freedom $s$ this approximation
of the solvation energy, justified to some extent for sufficiently
rigid solutes, does not hold for systems with a large number $n\to\infty$
of explicit water molecules outside of the tightly bound first solvation
shell. Indeed, in a gedanken experiment the difference $G[(\text{H}_{2}\text{O})_{n}]-nG[\text{H}_{2}\text{O}]$
for the above definition of $G$ applied to water droplets asymptotically
approaches $n(\bar{E}[\text{H}_{2}\text{O}]-G[\text{H}_{2}\text{O}])$
where $\bar{E}$ is the average configurational energy of a water
molecule; its value is about $-$9.9~kcal/mol \citep{Berendsen87,Mahoney00}.
This result is to be compared to the solvation energy of $-$6.3~kcal/mol
derived from the ratio of the equilibrium vapor/liquid concentrations
\citep{Bridgeman64}.

@@

Indeed, the behavior of another convolution operand at low $k$, the
solvent susceptibility is regular 
\begin{equation}
\tilde{\chi}_{\alpha\gamma}(k)\sim\rho\kappa+\frac{1}{2}d_{\alpha\gamma}k^{2}
\end{equation}
with the limit for $k\to0$ being proportional to the solvent compressibility
$\kappa$ (here in temperature units) \citep{book:Hansen06}. More
importantly, this limit is the same for all site pairs $\alpha$ and
$\gamma$. Though not enforced, this property is obeyed with reasonable
accuracy in practical calculations. The second term, of $o(k^{2})$,
is site pair specific and is in particular responsible for the dielectric
response of the solvent. This term is addressed by the dielectric
correction in the DRISM approach \citep{Perkyns92,Cummings81,Kovalenko00b}.
The result of the convolution, 
\begin{equation}
\tilde{\tau}_{\alpha}(\vec{k})=\tilde{n}(\vec{k})\tilde{\theta}_{\alpha}(k)\label{eq:tau}
\end{equation}
expressed here via the regular auxiliary functions
\begin{equation}
\tilde{\theta}_{\alpha}(k)=\tilde{\varphi}(k)\sum_{\gamma}\tilde{\chi}_{\alpha\gamma}(k)q_{\gamma}\sim2\pi\sum_{\gamma}d_{\alpha\gamma}q_{\gamma}\label{eq:theta}
\end{equation}
is also regular for an overall neutral solvent, $\sum_{\gamma}q_{\gamma}=0$.
In that case, the compressibility term in Eq.~\ref{eq:theta} vanishes
after summation. Note that the functions $\tilde{\theta}_{\alpha}(k)$
(one per solvent site $\alpha$) are convolutions of spherically symmetric
functions neither of which is solute specific. The functions $\tilde{\theta}_{\alpha}(k)$
are site-specific solvent properties which represent the response
to a unit charge (here broadened as a Gaussian). These quantities
can be computed using 1D techniques, just as the solvent susceptibility
$\tilde{\chi}_{\alpha\gamma}(k)$ itself. In the 1D case our deliberate
choice of the self-inverse discrete sine transform of type IV (DST-IV)
as a basic operation eliminates the need for treating the singularities
at $r=0$ and $k=0$ as the discrete representation does not include
these points by construction \citep{FFTW05}. A similar approach was
applied before to a monopole field of the solute \citep{Kloss08b}
and to a superposition of Gaussian-type charge distributions \citep{Perkyns10}.

@@

\begin{figure}[tbph]
\caption{Potential of mean force, $W(\varrho,z)$, for the
U--O$_{\text{w}}$ distribution function, determined with the closure
PSE1. $\varrho$ and $z$ are the radial and axial displacements from
the uranium center. \label{fig:potential-of-mean-force-2d}}
